Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-03-20 paper-RMDON.tex
Generando nuevo pdf con las referencias de Raquel
adding 3 more references to paper-RMDON.tex

\bibitem{takada-sakamura} H.~Takada and K.~Sakamura, \emph{Real-time synchronization protocols with abortable critical sections}. 1994 Proceedings of 1st International Workshop on Real-time Computing Systems & Application, pp. 48-52

@@

>>>>

\bibitem{takada-sakamura} H.~Takada and K.~Sakamura, \emph{Real-time synchronization protocols with abortable critical sections}. 1994 Proceedings of 1st International Workshop on Real-time Computing Systems \& Application, pp. 48-52

@@

\bibitem{tianzhou-jiangwei-lingxiang-xinliang}C.~Tianzhou, H.~Jiangwei, X.~Lingxiang and W.~Xinliang, \emph{Balance the battery life and real-time issues for portable real-time embedded system by applying DVS with battery model}, 34th Annual Conference of IEEE, Florida Hotel & Conference Center, FL, 2008. doi: 10.1109/IECON.2008.4758018

\bibitem{luo-jha}J.~Luo and N.K.~Jha, \emph{Balance the battery life and real-time issues for portable real-time embedded system by applying DVS with battery model}, IEEE/ACM International Conference on Computer Aided Design, San Jose, CA, 2000. doi: 10.1109/ICCAD.2000.896498

\bibitem{hung-chen-kuo}C.~Hung, J.~Chen and T.~Kuo, \emph{Energy-Efficient Real-Time Task Scheduling for a DVS System with a Non-DVS Processing Element},  Real-Time Systems Symposium, 27th IEEE International, Rio de Janeiro, Brazil, 2006. doi: 10.1109/RTSS.2006.22
